Using cosmic variance to constrain the dark matter halo mass and occupation fraction of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-06-23 paper/ms.tex
thinking

\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Using cosmic
  variance to constrain the dark matter halo mass of Lyman-alpha
  emitting galaxies at $z$=3.1}

@@

This mass scale is strictly superior to the all the $M_{\rm max}$
values allowed in the consistent models. Using the results published
in \cite{Behroozi2013a} we find that the typical stellar mass in halos
of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
their star formion rate is in the range $0.6\pm 0.2$ Msun yr$^{-1}$. These halo
masses actually correspond to the lower bound of what is computed in
the abundance matching model in order to fit the observational data
for the stellar mass function.

@@

... Intrinsic emission and escape fraction.

... Star formation rate efficiency at this redshift.

... Mass dependence of the escape fraction.

... Discuss all this in terms of the star formation efficiency in
Behroozi et al.

>>>>

\title[Halo mass and occupation fraction for LAEs at $z=3.1$]{Using cosmic
  variance to constrain the dark matter halo mass and occupation
  fraction of Lyman-alpha emitting galaxies at $z$=3.1}

@@

This mass scale is strictly superior to the all the $M_{\rm max}$
values allowed in the consistent models. Using the results published
in \cite{Behroozi2013a} we find that the typical stellar mass in halos
of $10^{11.4}$\hMsun is $(1.0\pm0.3)\times 10^{9.0}$ \hMsun, while
their star formion rate is in the range $0.6\pm 0.2$ Msun
yr$^{-1}$.  This halo mass range around $10^{11.4}$ \hMsun is the
lower bound of what is computed in the abundance matching model in
order to fit the observational data for the stellar mass function
based on the obervations of Lyman Break Galaxies.

@@

%... Intrinsic emission and escape fraction.

%... Star formation rate efficiency at this redshift.

%... Mass dependence of the escape fraction.

%... Discuss all this in terms of the star formation efficiency in
Behroozi et al.
